Kung Faux Pandas \\ \large Simplifying privacy protection

### 2018-11-08 paper/amia.tex
Auto Update from local Sharelatex

some text \\ and some more text \\ test

\begin{table}
   \caption{Summary of Included Data Synthesis Methods}
   \label{included-methods}
   \centering
   \begin{tabular}{p{12em} l p{20em}}
     \toprule
     Method                                 & Source                    & Notes \\
     \midrule
     %row 1 column 1
     Kernel Density Estimator; independent attribute mode
     %row 1 column 2
     & scipy.stats.gaussian\_kde
     %row 1 column 3
     & Creates a Gaussian Kernel Density Estimator using the Silverman method; fast but doesn’t maintain correlation between variables of the same observation.\\
     %row 2 column 1
     Kernel Density Estimator; correlated attribute mode &
     %row 2 column 2
     scipy.stats.gaussian\_kde &
     %row 2 column 3
     Creates a Gaussian Kernel Density Estimator across all variables per observation using a kde.factor of 0.01 \\
     %row 3 column 1
     DataSynthesizer; independent attribute mode
     %row 3 column 2
     & Ping et al.
     %row 3 column 3
     & A histogram is derived for each attribute, noise is added to the histogram to achieve differential privacy, and then samples are drawn for each attribute; fast but doesn’t maintain correlation between variables of the same observation.\\
     %row 4 column 1
     DataSynthesizer; correlated attribute mode
     %row 4 column 2
     & Ping et al.
     %row 4 column 3
     & Data is generated through a differentially private Bayesian network capturing the correlation between attributes. Computationally expensive and requires larger input dataset compared to independent attribute mode.\\
     \bottomrule
   \end{tabular}
 \end{table}

@@

Table~\ref{timing_results} documents results obtained from running the various plugins. Source code for running these performance tests are available in the Jupyter notebook performance\_tests.ipynb. The "Trivial" method provides a baseline comparison for evaluating the overhead of Pandas and correct input/output of the plugin class and function overloading mechanism; it returns the input data frame unmodified. The KDE methods leveraging scipy.stats.gaussian\_kde act as an example of how to create plugins. A couple of DataSynthesizer (abbreviated DS in the table) modes are used to demonstrate performance differences as well as generated synthetic data differences. "Independent" mode generates synthetic data with each attribute being modeled independently from the others. "Correlated" attribute mode finds inter-column relationships to more accurately generate synthetic data. Both DataSynthesizer modes are run with no configuration and again "w/Config" by passing in some column-wise dataset specific configuration.

\begin{table}
	\caption{Kung Faux Pandas data synthesis plugin timings (mean seconds)}
	\label{timing_results}
	\centering
	\begin{tabular}{l c c c c c}
		\toprule 
		Method & 10 rows & 100 rows & 1000 rows & 10000 rows & 100000 rows\\ 
		\midrule 
		Trivial & 2.5e-06 & 2.3e-06 & 2.3e-06 & 2.2e-06 & 2.2e-06 \\ 
		KDE & 0.086 & 0.079 & 0.074 & 0.074 & 0.122 \\ 
		DS Independent & 0.044 & 0.050 & 0.103 & 0.268 & 2.608 \\ 
		DS Independent w/Config & 0.045 & 0.040 & 0.064 & 0.120 & 0.799 \\
		DS Correlated & 0.188 & 1.419 & 3.460 & 16.66 & 159.9 \\ 
		DS Correlated w/Config & 0.172 & 0.627 & 1.393 & 342.7 & 2124 \\ 
		\midrule
	\end{tabular}
\end{table}

>>>>

\begin{table}
   \caption{Summary of Included Data Synthesis Methods}
   \label{included-methods}
   \centering
   \begin{tabular}{p{12em} l p{20em}}
     \toprule
     Method                                 & Source                    & Notes \\
     \midrule
     %row 1 column 1
     Kernel Density Estimator; independent attribute mode
     %row 1 column 2
     & scipy.stats.gaussian\_kde
     %row 1 column 3
     & Creates a Gaussian Kernel Density Estimator using the Silverman method; fast but doesn’t maintain correlation between variables of the same observation.\\
     %row 2 column 1
     Kernel Density Estimator; correlated attribute mode &
     %row 2 column 2
     scipy.stats.gaussian\_kde &
     %row 2 column 3
     Creates a Gaussian Kernel Density Estimator across all variables per observation using a kde.factor of 0.01 \\
     %row 3 column 1
     DataSynthesizer; independent attribute mode
     %row 3 column 2
     & Ping et al.
     %row 3 column 3
     & A histogram is derived for each attribute, noise is added to the histogram to achieve differential privacy, and then samples are drawn for each attribute; fast but doesn’t maintain correlation between variables of the same observation.\\
     %row 4 column 1
     DataSynthesizer; correlated attribute mode
     %row 4 column 2
     & Ping et al.
     %row 4 column 3
     & Data is generated through a differentially private Bayesian network capturing the correlation between attributes. Computationally expensive and requires larger input dataset compared to independent attribute mode.\\
     \bottomrule
   \end{tabular}
   \vspace{+3mm}
 \end{table}

@@

Table~\ref{timing_results} documents results obtained from running the various plugins. Source code for running these performance tests are available in the Jupyter notebook performance\_tests.ipynb. The "Trivial" method provides a baseline comparison for evaluating the overhead of Pandas and correct input/output of the plugin class and function overloading mechanism; it returns the input data frame unmodified. The KDE methods leveraging scipy.stats.gaussian\_kde act as an example of how to create plugins. Additionally the independent vs correlated KDE methods offer different accommodations for performance with correlated vs non-correlated source data. A couple of DataSynthesizer (abbreviated DS in the table) modes are used to demonstrate performance differences as well as generated synthetic data differences. "Independent" mode generates synthetic data with each attribute being modeled independently from the others. "Correlated" attribute mode finds inter-column relationships to more accurately generate synthetic data. Both DataSynthesizer modes are run with no configuration and again "w/Config" by passing in some column-wise dataset specific configuration.

\begin{table}
	\caption{Kung Faux Pandas data synthesis plugin timings (mean seconds)}
	\label{timing_results}
	\centering
	\begin{tabular}{l c c c c c}
		\toprule 
		Method & 10 rows & 100 rows & 1000 rows & 10000 rows & 100000 rows\\
		\midrule 
		Trivial & 2.5e-06 & 2.3e-06 & 2.3e-06 & 2.2e-06 & 2.2e-06 \\
		KDE Independent & 0.086 & 0.079 & 0.074 & 0.074 & 0.122 \\
		KDE Correlated & 0.017 & 0.021 & 0.027 & 2.43 & 120.8 \\
		DS Independent & 0.044 & 0.050 & 0.103 & 0.268 & 2.608 \\
		DS Independent w/Config & 0.045 & 0.040 & 0.064 & 0.120 & 0.799 \\
		DS Correlated & 0.188 & 1.419 & 3.460 & 16.66 & 159.9 \\
		DS Correlated w/Config & 0.172 & 0.627 & 1.393 & 342.7 & 2124 \\
		\midrule
	\end{tabular}
	\vspace{-4mm}
\end{table}
